cardinalR: Generating interesting high-dimensional data structures

### 2025-10-03 paper-cardinalR.Rmd
Removed Gaussian images

The `gen_gaussian(n, p, s)` function generates a multivariate Gaussian cloud in $p\text{-}D$, centered at the origin with user-defined covariance structure (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:gau)"} else { "Figure \\@ref(fig:gau-proj)"})`). Each point is independently drawn using the multivariate normal distribution with $X_i \sim N_p(\boldsymbol{0}, s)$, where $s$ is a user-defined $p \times p$ positive-definite matrix.

@@

```{r}
gau_lang <- langevitour::langevitour(gau, levelColors = "black", enableControls = FALSE, width = "400px", height = "300px")
```

```{r gau-proj1}
scaled_data <- scale_data_manual(gau)

gau_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r gau-proj2}

gau_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r gau-proj3}

gau_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r gau, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `gau` data in $4\\text{-}D$."}

gaufig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    gau_lang
  ),
  device = "xs"
)

class(gaufig) <- c(class(gaufig), "htmlwidget")

gaufig
```

```{r gau-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gau` data."}
#| fig-width: 12
#| fig-height: 4

gau_proj1 + gau_proj2 + gau_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

>>>>

The `gen_gaussian(n, p, s)` function generates a multivariate Gaussian cloud in $p\text{-}D$, centered at the origin with user-defined covariance structure. Each point is independently drawn using the multivariate normal distribution with $X_i \sim N_p(\boldsymbol{0}, s)$, where $s$ is a user-defined $p \times p$ positive-definite matrix.

@@

### 2025-10-03 paper-cardinalR.tex
Removed Gaussian images

The \texttt{gen\_gaussian(n,\ p,\ s)} function generates a multivariate Gaussian cloud in \(p\text{-}D\), centered at the origin with user-defined covariance structure (Figure \ref{fig:gau-proj}). Each point is independently drawn using the multivariate normal distribution with \(X_i \sim N_p(\boldsymbol{0}, s)\), where \(s\) is a user-defined \(p \times p\) positive-definite matrix.

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/gau-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gau` data.}\label{fig:gau-proj}
\end{figure}

>>>>

The \texttt{gen\_gaussian(n,\ p,\ s)} function generates a multivariate Gaussian cloud in \(p\text{-}D\), centered at the origin with user-defined covariance structure. Each point is independently drawn using the multivariate normal distribution with \(X_i \sim N_p(\boldsymbol{0}, s)\), where \(s\) is a user-defined \(p \times p\) positive-definite matrix.

@@
